---
title: "Bachelor Supply and the Unemployment Gap in Canada"
author: "Arka Dev Biswas Deepra, Dominic Muhimfura"
date: "`r Sys.Date()`"
output:
  github_document:
    toc: true
  html_document:
    toc: true
    toc_float: true
    code_folding: show
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Introduction
This document presents the empirical analysis for the paper "Do the relative supply of bachelor's graduates affect the unemployment gap between degree holders and non-degree holders in Canada?" Using Statistics Canada's Labour Force Survey (LFS) from 2006 to 2025, we estimate linear probability models, probit models, and an aggregate province‑year panel regression to examine whether rising bachelor supply erodes the unemployment advantage of degree holders.

**Data availability:** This analysis uses Statistics Canada's Labour Force Survey Public Use Microdata File (PUMF). The raw microdata is not included in this repository — check Statistics Canada's licensing terms before redistributing it, and download it directly from [Statistics Canada](https://www.statcan.gc.ca/) if you want to reproduce these results. Place the file at `data/EVERMD.csv` relative to this document (see below), or update `DATA_PATH`.

# Setup and Data Loading
We first load required packages and define file paths. `DATA_PATH` and `OUTPUT_DIR` are relative to the project root, so this should run as-is after cloning the repo — just make sure the LFS CSV is placed at `data/EVERMD.csv`.

```{r}
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(readr)
library(fixest)
library(modelsummary)
library(patchwork)
library(scales)
library(data.table)
```


```{r paths, echo=FALSE}
# Since the RMD is in the Codes folder, go up one level to project root
DATA_PATH  <- "../data/EVERMD.csv"
OUTPUT_DIR <- "../results"
if (!dir.exists(OUTPUT_DIR)) dir.create(OUTPUT_DIR, recursive = TRUE)
out <- function(f) file.path(OUTPUT_DIR, f)
```

# Helper functions
We define a table‑saving function that uses ggplot2 to create clean PNG images of regression tables.

```{r}
save_table <- function(df, filepath, title = NULL, note = NULL) {
  df <- as.data.frame(df)
  drop <- tolower(names(df)) %in% c("part", "statistic", "n")
  df   <- df[, !drop, drop = FALSE]
  names(df)[1] <- "Variable"
  df[sapply(df, is.numeric)] <- lapply(df[sapply(df, is.numeric)], round, 3)
  df[] <- lapply(df, as.character)
  
  nc <- ncol(df); nr <- nrow(df)
  cw <- c(2.6, rep(1.0, nc - 1))
  
  cells <- rbind(
    data.frame(row=0, col=seq_len(nc), label=colnames(df), is_hdr=TRUE),
    do.call(rbind, lapply(seq_len(nr), function(r)
      data.frame(row=r, col=seq_len(nc), label=unlist(df[r,]), is_hdr=FALSE)))
  )
  cells$fill  <- ifelse(cells$is_hdr, "#EAF1F8",
                        ifelse(cells$row %% 2 == 1, "#F7FAFD", "#FFFFFF"))
  cells$y     <- (nr + 0.5) - cells$row
  cells$x_pos <- sapply(cells$col, function(c) sum(cw[seq_len(c-1)]) + cw[c]/2)
  x_max <- sum(cw)
  t_gap <- if (!is.null(title)) 0.9 else 0
  n_gap <- if (!is.null(note))  0.5 else 0
  
  p <- ggplot(cells, aes(x=x_pos, y=y)) +
    geom_tile(aes(fill=fill, width=cw[col]), colour="grey75", linewidth=0.25) +
    geom_text(aes(label=label,
                  fontface=ifelse(is_hdr,"bold","plain"),
                  colour=ifelse(is_hdr,"#1A3F5C","grey15")),
              size=3.0, hjust=0,
              nudge_x=-sapply(cells$col, function(c) cw[c]/2 - 0.07)) +
    scale_fill_identity() + scale_colour_identity() +
    scale_x_continuous(expand=c(0,0), limits=c(0, x_max)) +
    scale_y_continuous(expand=c(0,0), limits=c(-n_gap, nr+0.5+t_gap)) +
    theme_void() +
    theme(plot.background=element_rect(fill="white", colour=NA),
          plot.margin=margin(8,12,8,12))
  
  if (!is.null(title))
    p <- p + annotate("text", x=0, y=nr+0.5+t_gap*0.85, label=title,
                      hjust=0, vjust=0.5, size=3.8, fontface="bold", colour="#1A3F5C")
  if (!is.null(note))
    p <- p + annotate("text", x=0, y=-n_gap*0.7, label=note,
                      hjust=0, vjust=0.5, size=2.4, fontface="italic", colour="grey45")
  
  ggsave(filepath, p,
         width  = max(7, x_max + 0.5),
         height = max(2, (nr + 1.5 + t_gap + n_gap) * 0.38),
         dpi=150, bg="white")
}
```

# Province and industry labels
```{r}
prov_labels <- c(
  "10"="NL","11"="PEI","12"="NS","13"="NB",
  "24"="QC","35"="ON","46"="MB","47"="SK","48"="AB","59"="BC"
)

naics_labels <- c(
  "01"="Agriculture","02"="Forestry & Logging","03"="Fishing, Hunting & Trapping",
  "04"="Mining & Oil/Gas","05"="Utilities","06"="Construction",
  "07"="Manufacturing - Durable","08"="Manufacturing - Non-Durable",
  "09"="Wholesale Trade","10"="Retail Trade","11"="Transportation & Warehousing",
  "12"="Finance & Insurance","13"="Real Estate","14"="Professional & Scientific",
  "15"="Business & Support Services","16"="Educational Services",
  "17"="Health Care & Social Assistance","18"="Information & Culture",
  "19"="Accommodation & Food","20"="Other Services","21"="Public Administration"
)
```

# Data Preparation
## Load raw data
We read the LFS public use microdata file and standardize column names to lowercase.
```{r}

dt <- fread(DATA_PATH, na.strings = "")
dt <- as_tibble(dt)

# Standardize column names
names(dt) <- tolower(names(dt))

keep_cols <- c("survyear", "survmnth", "finalwt", "lfsstat", "educ", "prov", 
               "naics_21", "immig", "age_12", "age_6")
missing_cols <- setdiff(keep_cols, names(dt))
if (length(missing_cols) > 0) {
  stop("Missing columns: ", paste(missing_cols, collapse = ", "))
}
dt <- dt %>% select(all_of(keep_cols))
if (!is.numeric(dt$finalwt)) dt$finalwt <- as.numeric(dt$finalwt)

cat("Loaded:", nrow(dt), "rows\n")
```

## Apply age filter (22+) and build panels
We restrict the sample to individuals aged 22 and older, exclude postgraduates (educ == 6), and construct national and province‑level aggregates.
```{r}
base <- dt %>%
  filter(!educ %in% c(6)) %>%
  mutate(
    date = make_date(survyear, survmnth, 1),
    age_12_num = as.numeric(age_12),
    age_6_num  = as.numeric(age_6)
  ) %>%
  filter(
    (age_6_num %in% 4:6) | (age_12_num %in% 3:12)
  )

agg_cols <- function(grp) {
  grp %>% summarise(
    bach_lf        = sum(finalwt[educ==5  & lfsstat %in% c(1,2,3)], na.rm=TRUE),
    nobach_lf      = sum(finalwt[!educ %in% c(5,6) & lfsstat %in% c(1,2,3)], na.rm=TRUE),
    bach_emp       = sum(finalwt[educ==5  & lfsstat %in% c(1,2)], na.rm=TRUE),
    nobach_emp     = sum(finalwt[!educ %in% c(5,6) & lfsstat %in% c(1,2)], na.rm=TRUE),
    total_emp      = sum(finalwt[lfsstat %in% c(1,2)], na.rm=TRUE),
    bach_unemp     = sum(finalwt[educ==5  & lfsstat==3], na.rm=TRUE),
    nobach_unemp   = sum(finalwt[!educ %in% c(5,6) & lfsstat==3], na.rm=TRUE),
    immig_lf_share = sum(finalwt[immig %in% c(2,3) & lfsstat %in% c(1,2,3)], na.rm=TRUE) /
                     sum(finalwt[lfsstat %in% c(1,2,3)], na.rm=TRUE),
    .groups="drop"
  ) %>%
    mutate(
      bach_u_rate    = bach_unemp   / bach_lf,
      nobach_u_rate  = nobach_unemp / nobach_lf,
      unemp_gap      = bach_u_rate - nobach_u_rate,
      bach_density   = bach_emp   / total_emp,
      nobach_density = nobach_emp / total_emp
    ) %>%
    mutate(across(where(is.numeric), ~ifelse(is.infinite(.) | is.nan(.), NA, .)))
}

agg        <- base %>% group_by(date) %>% agg_cols()
prov_panel <- base %>% group_by(date, prov) %>% agg_cols() %>%
  mutate(
    year      = year(date),
    prov_name = recode(as.character(prov), !!!prov_labels)
  ) %>%
  filter(bach_lf > 100, nobach_lf > 100)

cat("National:", nrow(agg), "months | Province panel:", nrow(prov_panel), "cells\n")

```

## Individual‑level dataset
```{r}
indiv <- dt %>%
  filter(!educ %in% c(6)) %>%
  mutate(
    age_12_num = as.numeric(age_12),
    age_6_num  = as.numeric(age_6)
  ) %>%
  filter(
    (age_6_num %in% 4:6) | (age_12_num %in% 3:12)
  ) %>%
  mutate(
    date       = make_date(survyear, survmnth, 1),
    employed   = if_else(lfsstat %in% c(1,2), 1L, 0L),
    unemployed = if_else(lfsstat == 3, 1L, 0L),
    is_bach    = if_else(educ == 5, 1L, 0L),
    is_immig   = if_else(immig %in% c(2,3), 1L, 0L)
  ) %>%
  filter(!is.na(employed)) %>%
  left_join(
    agg %>% select(date, bach_density, nobach_density, unemp_gap, immig_lf_share),
    by = "date"
  ) %>%
  mutate(bach_interaction = is_bach * bach_density)
```

# Descriptive Statistics
We produce several tables summarizing the composition of the labour force and unemployment rates over time and across provinces.

```{r}
# D1: Labour force composition
tab_D1 <- agg %>% mutate(yr=year(date)) %>% group_by(yr) %>%
  summarise(bach_lf_n=round(mean(bach_lf, na.rm=TRUE)),
            nobach_lf_n=round(mean(nobach_lf, na.rm=TRUE)),
            bach_share_pct=round(100*mean(bach_lf/(bach_lf+nobach_lf), na.rm=TRUE),2),
            .groups="drop")
write.csv(tab_D1, out("desc_D1_bach_number_share.csv"), row.names=FALSE)

# D2: Unemployment rates and gap
tab_D2 <- agg %>% mutate(yr=year(date)) %>% group_by(yr) %>%
  summarise(bach_u_pct=round(100*mean(bach_u_rate, na.rm=TRUE),2),
            nobach_u_pct=round(100*mean(nobach_u_rate, na.rm=TRUE),2),
            gap_pp=round(100*mean(unemp_gap, na.rm=TRUE),2),
            .groups="drop")
write.csv(tab_D2, out("desc_D2_urates_by_group.csv"), row.names=FALSE)

# D3: Combined with immigration share
tab_D3 <- left_join(tab_D1, tab_D2, by="yr") %>%
  left_join(agg %>% mutate(yr=year(date)) %>% group_by(yr) %>%
              summarise(immig_share_pct=round(100*mean(immig_lf_share, na.rm=TRUE),2),
                        .groups="drop"), by="yr")
write.csv(tab_D3, out("desc_D3_tabulation_over_time.csv"), row.names=FALSE)

# D5: Province summary
tab_D5 <- prov_panel %>% filter(!is.na(prov_name)) %>% group_by(prov_name) %>%
  summarise(n_months=n(),
            bach_share_pct=round(100*mean(bach_lf/(bach_lf+nobach_lf), na.rm=TRUE),2),
            bach_u_pct=round(100*mean(bach_u_rate, na.rm=TRUE),2),
            nobach_u_pct=round(100*mean(nobach_u_rate, na.rm=TRUE),2),
            gap_pp=round(100*mean(unemp_gap, na.rm=TRUE),2),
            immig_share_pct=round(100*mean(immig_lf_share, na.rm=TRUE),2),
            .groups="drop") %>%
  arrange(desc(bach_share_pct))
write.csv(tab_D5, out("desc_D5_province_summary.csv"), row.names=FALSE)

# D6: Correlation matrix
agg %>% select(unemp_gap, bach_density, nobach_density, bach_u_rate, nobach_u_rate, immig_lf_share) %>%
  filter(complete.cases(.)) %>% cor() %>% round(3) %>% as.data.frame() %>%
  write.csv(out("desc_D6_correlation_matrix.csv"), row.names=TRUE)

# D7a: Aggregate summary stats
datasummary((`Unemp Gap (pp) [Bach - Non-Bach]`=I(unemp_gap*100)) +
              (`Bach U-Rate (%)`=I(bach_u_rate*100)) + (`Non-Bach U-Rate (%)`=I(nobach_u_rate*100)) +
              (`Bach LF Share (%)`=I(bach_density*100)) + (`Non-Bach LF Share (%)`=I(nobach_density*100)) +
              (`Immigrant LF Share (%)`=I(immig_lf_share*100)) ~ Mean+SD+Min+Median+Max,
            data=agg, output="data.frame") %>%
  save_table(out("desc_D7a_aggregate.png"),
             title="Table D7a: Summary Statistics — National Aggregate Panel",
             note=paste0("N=", nrow(agg), " monthly obs. FINALWT-weighted."))

# D7b: Individual‑level summary stats
datasummary((`Employed (0/1)`=employed) + (`Bachelor (0/1)`=is_bach) + (`Immigrant (0/1)`=is_immig) +
              (`Bach LF Share (%)`=I(bach_density*100)) + (`Non-Bach LF Share (%)`=I(nobach_density*100)) +
              (`Unemp Gap (pp)`=I(unemp_gap*100)) ~ Mean+SD+Min+Median+Max,
            data=indiv, weights=~finalwt, output="data.frame") %>%
  save_table(out("desc_D7b_individual.png"),
             title="Table D7b: Summary Statistics — Individual-Level Sample",
             note=paste0("N=", format(nrow(indiv), big.mark=","), " respondents. FINALWT-weighted."))
```

# Plots
## Unemployment gap over time
```{r}
p1 <- ggplot(agg, aes(date, unemp_gap)) +
  geom_hline(yintercept=0, linetype="dotted", colour="grey50") +
  geom_line(colour="#2C5F8A", linewidth=0.8) +
  geom_smooth(method="loess", se=TRUE, colour="#E05C1A", linetype="dashed") +
  scale_y_continuous(labels=percent_format(accuracy=0.1)) +
  labs(x=NULL, y="Unemployment Rate Gap (pp)") +
  theme_minimal(base_size=13)
ggsave(out("unemp_gap_time.png"), p1, width=9, height=5, dpi=150)
p1
```

## Bachelor share of employment over time

```{r}
p2 <- ggplot(agg, aes(date, bach_density)) +
  geom_line(colour="#2C5F8A", linewidth=0.8) +
  geom_smooth(method="loess", se=TRUE, colour="#E05C1A", linetype="dashed") +
  scale_y_continuous(labels=percent_format(accuracy=1)) +
  labs(x=NULL, y="Bachelor Share") +
  theme_minimal(base_size=13)
ggsave(out("bach_density_time.png"), p2, width=9, height=5, dpi=150)
p2
```

## Unemployment rates by education group

```{r}
p3c <- indiv %>%
  mutate(yr = year(date)) %>%
  group_by(yr, is_bach) %>%
  summarise(u_rate = weighted.mean(unemployed, finalwt, na.rm = TRUE), .groups = "drop") %>%
  mutate(group = if_else(is_bach == 1, "Bachelor", "Non-Bachelor")) %>%
  ggplot(aes(x = factor(yr), y = u_rate, fill = group)) +
  geom_col(position = position_dodge(0.7), width = 0.65, alpha = 0.88) +
  scale_y_continuous(labels = percent_format(accuracy = 0.1)) +
  scale_fill_manual(values = c("Bachelor" = "#2C5F8A", "Non-Bachelor" = "#E05C1A")) +
  labs(x = "Year", y = "Unemployment Rate", fill = NULL) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid.major.x = element_blank())
ggsave(out("urates_by_group_time.png"), p3c, width = 9, height = 5, dpi = 150)
p3c
```

## Province‑level heterogeneity
```{r}
p4 <- prov_panel %>% filter(!is.na(prov_name)) %>% group_by(prov_name, year) %>%
  summarise(unemp_gap=mean(unemp_gap, na.rm=TRUE), bach_density=mean(bach_density, na.rm=TRUE), .groups="drop") %>%
  ggplot(aes(bach_density, unemp_gap, colour=prov_name)) +
  geom_point(alpha=0.5, size=1.5) +
  geom_smooth(method="lm", se=FALSE, linewidth=0.6) +
  facet_wrap(~prov_name, scales="free") +
  labs(x="Bachelor Share", y="Unemployment Gap (pp)") +
  theme_minimal(base_size=11) + theme(legend.position="none")
ggsave(out("province_heterogeneity.png"), p4, width=12, height=9, dpi=150)
p4
```

## Industry employment rates
```{r}
indiv <- indiv %>%
  mutate(industry = factor(naics_21, levels = names(naics_labels), labels = naics_labels))

industry_data <- indiv %>%
  filter(!is.na(industry)) %>%
  group_by(industry, is_bach) %>%
  summarise(emp_rate = weighted.mean(employed, finalwt, na.rm = TRUE), n = n(), .groups = "drop") %>%
  filter(n >= 100)

if (nrow(industry_data) == 0) stop("No industry groups meet the sample size threshold.")

industry_wide <- industry_data %>%
  pivot_wider(id_cols = industry, names_from = is_bach, values_from = emp_rate, names_prefix = "bach_") %>%
  rename(bach_rate = bach_1, nobach_rate = bach_0) %>%
  filter(!is.na(bach_rate) & !is.na(nobach_rate)) %>%
  mutate(industry = reorder(industry, bach_rate))

p5 <- ggplot(industry_wide, aes(y = industry)) +
  geom_segment(aes(x = nobach_rate, xend = bach_rate, yend = industry), colour = "grey60", linewidth = 0.6) +
  geom_point(aes(x = nobach_rate, colour = "Non-Bachelor"), size = 3, shape = 17) +
  geom_point(aes(x = bach_rate, colour = "Bachelor"), size = 3, shape = 16) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_colour_manual(name = NULL, values = c("Bachelor" = "#2C5F8A", "Non-Bachelor" = "#E05C1A")) +
  labs(x = "Employment Rate", y = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", axis.text.y = element_text(size = 9),
        panel.grid.major.y = element_blank(), panel.grid.minor = element_blank())
ggsave(out("industry_heterogeneity.png"), p5, width = 11, height = 9, dpi = 150)
p5
```
## Provincial composition (bachelor share and employment gap)
```{r}
prov_order <- indiv %>% mutate(prov_name=recode(as.character(prov), !!!prov_labels)) %>%
  filter(!is.na(prov_name)) %>% group_by(prov_name) %>%
  summarise(pct=100*sum(finalwt[is_bach==1])/sum(finalwt), .groups="drop") %>%
  arrange(desc(pct)) %>% pull(prov_name)

comp_prov <- indiv %>% mutate(prov_name=recode(as.character(prov), !!!prov_labels)) %>%
  filter(!is.na(prov_name)) %>% group_by(prov_name) %>%
  summarise(pct_bach=round(100*sum(finalwt[is_bach==1])/sum(finalwt),1),
            emp_rate_bach=round(100*weighted.mean(employed[is_bach==1], finalwt[is_bach==1], na.rm=TRUE),1),
            emp_rate_nobach=round(100*weighted.mean(employed[is_bach==0], finalwt[is_bach==0], na.rm=TRUE),1),
            emp_gap_pp=round(emp_rate_bach - emp_rate_nobach,1), .groups="drop")

p7a <- comp_prov %>% mutate(prov_name=factor(prov_name, prov_order)) %>%
  ggplot(aes(prov_name, pct_bach, fill=pct_bach)) + geom_col(width=0.65, show.legend=FALSE) +
  geom_text(aes(label=paste0(pct_bach,"%")), vjust=-0.4, size=3.2) +
  scale_fill_gradient(low="#A8C8E8", high="#2C5F8A") +
  labs(x=NULL, y="Bach Share (%)") + theme_minimal(base_size=11)

p7b <- comp_prov %>% mutate(prov_name=factor(prov_name, prov_order)) %>%
  ggplot(aes(prov_name, emp_gap_pp, fill=emp_gap_pp)) + geom_col(width=0.65, show.legend=FALSE) +
  geom_text(aes(label=paste0(ifelse(emp_gap_pp>=0,"+",""), emp_gap_pp,"pp")), vjust=-0.4, size=3.2) +
  scale_fill_gradient2(low="#E05C1A", mid="grey90", high="#2C5F8A", midpoint=0) +
  labs(x="Province", y="Employment Gap (Bach minus Non-Bach, pp)") + theme_minimal(base_size=11)

p7 <- p7a / p7b + plot_layout(heights=c(1,1))
ggsave(out("province_composition.png"), p7, width=11, height=9, dpi=150)
p7
```

# Model Estimation
All models include the main effect of bachelor density (bach_density) alongside its interaction with bachelor status.

## Linear Probability Model with Interaction
```{r}
lpm_interaction <- feols(
  unemployed ~ is_bach + bach_density + bach_interaction + is_immig | prov + survyear + naics_21,
  data    = indiv,
  weights = ~finalwt,
  cluster = ~prov
)

modelsummary(
  list("Interaction LPM" = lpm_interaction),
  stars = TRUE,
  coef_map = c("is_bach" = "Bachelor", "bach_density" = "Bachelor Density",
               "bach_interaction" = "Bachelor × Density", "is_immig" = "Immigrant"),
  gof_map = list(
    list(raw = "nobs", clean = "N", fmt = function(x) format(round(x), big.mark = ",")),
    list(raw = "r.squared", clean = "Within R²", fmt = 3),
    list(raw = "adj.r.squared", clean = "Adj. Within R²", fmt = 3)
  ),
  output = "data.frame"
) %>%
  save_table(
    out("lpm_interaction_results.png"),
    title = "Unemployment Probability: LPM with Interaction",
    note  = paste0(
      "DV: Unemployed (1) / Not Unemployed (0). Includes province, year, and industry fixed effects. ",
      "FINALWT-weighted, province-clustered SE. *** p<0.01, ** p<0.05, * p<0.1. Postgrad excluded. Source: LFS 2006-2025."
    )
  )
```

## Aggregate Unemployment Gap Model (Province‑Year Panel)
```{r}
model_gap <- feols(
  unemp_gap ~ bach_density | prov + year,
  data = prov_panel,
  cluster = ~prov
)

modelsummary(
  list("Gap Model" = model_gap),
  stars = TRUE,
  gof_map = list(
    list(raw = "nobs", clean = "N (province-months)", fmt = function(x) format(round(x), big.mark = ",")),
    list(raw = "r.squared", clean = "Within R²", fmt = 3),
    list(raw = "adj.r.squared", clean = "Adj. Within R²", fmt = 3)
  ),
  output = "data.frame"
) %>%
  save_table(
    out("model4_gap_results.png"),
    title = "Aggregate Unemployment Gap (Province-Year Panel)",
    note  = paste0(
      "DV: Unemployment gap (Bach minus Non-Bach u-rate). Province and year FE included. ",
      "Province-clustered SE. *** p<0.01, ** p<0.05, * p<0.1."
    )
  )
```

## Probit Models
```{r}
probit_1 <- feglm(unemployed ~ is_bach + is_immig, data = indiv, weights = ~finalwt, family = binomial("probit"))
probit_2 <- feglm(unemployed ~ is_bach + bach_density + bach_interaction + is_immig, data = indiv, weights = ~finalwt, family = binomial("probit"))
probit_3 <- feglm(unemployed ~ is_bach + bach_density + bach_interaction + is_immig | prov + survyear, data = indiv, weights = ~finalwt, family = binomial("probit"))
probit_4 <- feglm(unemployed ~ is_bach + bach_density + bach_interaction + is_immig | prov + survyear + naics_21, data = indiv, weights = ~finalwt, family = binomial("probit"))

# Summary statistics for probit sample
m1_vars <- indiv %>% select(unemployed, is_bach, is_immig, bach_density, finalwt) %>% filter(complete.cases(.))
summary_stats_probit <- m1_vars %>%
  reframe(
    Variable = c("Unemployed (0/1)", "Bachelor (0/1)", "Immigrant (0/1)", "Bach Density (%)"),
    Mean = c(weighted.mean(unemployed, finalwt, na.rm=TRUE), weighted.mean(is_bach, finalwt, na.rm=TRUE),
             weighted.mean(is_immig, finalwt, na.rm=TRUE), weighted.mean(bach_density, finalwt, na.rm=TRUE)*100),
    SD = c(sd(unemployed), sd(is_bach), sd(is_immig), sd(bach_density)*100),
    Median = c(median(unemployed), median(is_bach), median(is_immig), median(bach_density)*100),
    Min = c(min(unemployed), min(is_bach), min(is_immig), min(bach_density)*100),
    Max = c(max(unemployed), max(is_bach), max(is_immig), max(bach_density)*100)
  ) %>% mutate(across(where(is.numeric), ~ round(., 3)))

save_table(summary_stats_probit, out("model1_summary_stats.png"),
           title = "Model 1 — Summary Statistics: Individual Probit Sample",
           note = paste0("N = ", format(nrow(m1_vars), big.mark=","), " respondents. FINALWT-weighted. Postgrad excluded."))

# Probit results table
modelsummary(
  list("Baseline" = probit_1, "+Supply" = probit_2, "+Prov/Year FE" = probit_3, "+Immig+Ind FE" = probit_4),
  stars = TRUE,
  coef_map = c("(Intercept)" = "Constant", "is_bach" = "Bachelor", "bach_density" = "Bachelor Density",
               "bach_interaction" = "Bachelor × Density", "is_immig" = "Immigrant"),
  gof_map = list(
    list(raw = "nobs", clean = "N", fmt = function(x) format(round(x), big.mark = ",")),
    list(raw = "logLik", clean = "Log-Likelihood", fmt = 2),
    list(raw = "r.squared", clean = "Pseudo R²", fmt = 3)
  ),
  output = "data.frame"
) %>%
  save_table(
    out("model1_probit_results.png"),
    title = "Probability of Unemployment (Probit)",
    note  = paste0(
      "Outcome: Unemployed (1) / Not Unemployed (0). FINALWT-weighted. ",
      "Spec 2 adds bachelor density and its interaction. Spec 3 adds province and year FE. ",
      "Spec 4 adds immigrant status and industry FE. Constant not identified in FE models. ",
      "*** p<0.01, ** p<0.05, * p<0.1. Postgrad excluded. Source: LFS."
    )
  )
```

# Conclusion
This document reproduces the entire empirical workflow of the paper. All tables and figures are saved in the specified output directory. The results consistently show that while bachelor holders maintain an unemployment advantage, that advantage erodes modestly as the relative supply of degree holders increases—evidence of mild crowding‑out at the individual level, contrasting with a widening aggregate gap driven by demand‑side factors.